Computing Entropies With Nested Sampling

### 2017-07-31 paper/ms.tex
Mention the tradeoff in choosing the distance threshold

If we actually want the differential entropy
\begin{align}
H(\x) &= -\int p(\x) \log p(\x) \, d\x
\end{align}
we can use the fact that density equals mass divided
by volume. Assume $r$ is small, so that
\begin{align}
P(d(\x; \xref) < r \,|\, \xref)
    &\approx
    p(\xref) \int_{d(\x; \xref) < r} \, d\x\\
    &= p(\xref) \, V
\end{align}
where $V$ is the volume of the region where $d(\x; \xref) < r$.
Then $H(\x) = \left< \depth \right>_{p(\x)} + \log V(r)$.

>>>>

If we actually want the differential entropy
\begin{align}
H(\x) &= -\int p(\x) \log p(\x) \, d\x
\end{align}
we can use the fact that density equals mass divided
by volume. Assume $r$ is small, so that
\begin{align}
P(d(\x; \xref) < r \,|\, \xref)
    &\approx
    p(\xref) \int_{d(\x; \xref) < r} \, d\x\\
    &= p(\xref) \, V
\end{align}
where $V$ is the volume of the region where $d(\x; \xref) < r$.
Then $H(\x) = \left< \depth \right>_{p(\x)} + \log V(r)$.
Reducing $r$ towards zero ought to lead to
a more accurate result because the probability density at a point will
be more accurately approximated by the probability of a small region containing
the point, divided by the volume of that region.
On the other hand, smaller values of $r$ will lead to more Nested Sampling
iterations required, and hence less accuracy in the depth estimates.
Thus, there is a an awkward trade-off involved in choosing the value of $r$,
which will need to be investigated more thoroughly in the future.
